Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting

### 2021-01-09 paper/paper.tex
Minor changes to paper

\title{Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting}
\title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
\author{Fabian Ritz Ratke$^{1}$, Daniel Ratke$^{1}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
\mbox{}\\
$^1$Mobile and Distributed Systems Group, LMU Munich, Germany \\
$^2$LMU Munich, Germany \\
D.Ratke@campus.lmu.de} % email of corresponding author

@@

\begin{figure*}%
    \centering
    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 5 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
    \caption{Cooperation rate in different scenarios. TODO: Analysis}%
    \label{fig:coop}%
\end{figure*}

>>>>

\title{Towards Ecosystem Management from Greedy Reinforcement Learning in a Predator-Prey Setting}
\title{Emergent Cooperation from Greedy Multi-Agent Reinforcement Learning in a Predator-Prey Setting}
\author{Fabian Ritz$^{1}$, Daniel Ratke$^{2}$, Thomy Phan$^1$ \and Claudia Linnhoff-Popien$^1$ \\
\mbox{}\\
$^1$Mobile and Distributed Systems Group, LMU Munich, Germany \\
$^2$LMU Munich, Germany \\
D.Ratke@campus.lmu.de} % email of corresponding author

@@

\begin{figure*}%
    \centering
    \subfloat[][\centering Cooperation rate with initial fish population of 5.]{\includegraphics[width=5.5cm]{figures/coop_chart_split1.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 10.]{\includegraphics[width=5.5cm]{figures/coop_chart_split2.png} }%
    \subfloat[][\centering Cooperation rate with initial fish population of 10 and stuns.]{\includegraphics[width=6.5cm]{figures/coop_chart_stuns_split2.png} }%
    \caption{Cooperation rate in different scenarios. TODO: Analysis}%
    \label{fig:coop}%
\end{figure*}
